---
title: 'Assignment 3: Bayesian ANOVA'
author: "Schwetlick"
date: '2018-05-02'
output: 
    html_document:
        toc: yes
        toc_depth: 3
        number_sections: no
fig_width: 12 
fig_height: 8 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
library(tidyverse)
library(BayesFactor)
```

# Task
Use the BayesFator package to analyse the data with a Bayesian ANOVA with the repeated measures.

```{r data}
load("../assignment/LooksOrPersonality.Rda")
head(LooksOrPersonality)
```
## a. Perform a Bayesian two-way ANOVA with the repeated measures Looks and Personality and calculate the bayes factors for all three effects (i.e., BFs when omitting from the full model).

```{r a}
bf = anovaBF(preference ~ looks*personality+subject_id, data=LooksOrPersonality, whichRandom="subject_id")
bf
# plot(bf)
# bf[4] is the full model, so we compare reduced models to it
bf/bf[4]
plot(bf/bf[4])
```

The full model is preferred over the reduced models. 

## b. Make the same analysis with an “ultrawide” Cauchy distribution as prior.
```{r b}
bf_wide = anovaBF(preference ~ looks*personality+subject_id, data=LooksOrPersonality, whichRandom="subject_id", rscaleFixed = "ultrawide")
bf_wide
# bf[4] is the full model, so we compare reduced models to it
bf_wide/bf_wide[4]
plot(bf_wide/bf_wide[4])
```

Still, the full model is preferred over the reduced models. 


## c. Please include also the factor Gender and test if there is evidence for a three-way
interaction Looks × Personality × Gender.
```{r fig.height = 16, fig.width = 48}
bf_g = anovaBF(preference ~ looks*personality*gender+subject_id, data=LooksOrPersonality, whichRandom="subject_id")
bf_g
# bf[18] is the full model, so we compare reduced models to it
bf_g/bf_g[18]
plot(bf_g/bf_g[18])

# check specifically for interaction
bf_g[17]/bf_g[18]
```

There is evidence for a three way interaction.

# Program version
```{r script_13}
sessionInfo()
````