---
title: 'Assignment 4: One-sample t-test in JAGS'
author: "Schwetlick"
date: '2018-05-02'
output: 
    html_document:
        toc: yes
        toc_depth: 3
        number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(BayesFactor)
```

Data: weight.csv
# A clinic provides a program to help their clients lose weight and asks you to investigate the effectiveness of the program. You have a sample of 15 people, weighing each person before the program begins and 3 months later.
Determine whether the program is effective. To do so, implement the t-test in JAGS and use a Cauchy distribution as prior.

```{r data}
weight<-read.csv("../assignment/weight.csv")
head(weight)
````

## a. Plot the posterior distribution of the δ parameter.

## b. Estimate the bayes factor between H0 : δ = 0 and H1 : δ ∼ Cauchy(0, 1) by using the Savage-Dickey method (see slides).

## c. Use both a normal and an “ultrawide” rscale parameter for the Cauchy prior distribution.

# Program version
```{r script_13}
sessionInfo()
````