---
title: 'Assignment 4: One-sample t-test in JAGS'
author: "Schwetlick"
date: '2018-05-02'
output: 
    html_document:
        toc: yes
        toc_depth: 3
        number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(BayesFactor)
setwd('/Users/lisa/Documents/BayesCourse/Potsdam-Bayes-2018/Lisa_Solutions')
library('rjags')
library('coda')
library('polspline')
source("kruschke-utilities.R")
```

Data: weight.csv
# A clinic provides a program to help their clients lose weight and asks you to investigate the effectiveness of the program. You have a sample of 15 people, weighing each person before the program begins and 3 months later.
Determine whether the program is effective. To do so, implement the t-test in JAGS and use a Cauchy distribution as prior.

```{r data}
weight<-read.csv("../assignment/weight.csv")
head(weight)
diffs<-weight$Before-weight$After
plot(diffs)

jags.data = list('x' = diffs,
                 'N' = length(diffs),
                 'rscale'=1) # width of the prior
# here we just say where to start sampling. Make it random
random.init = function() {
  list(delta = rnorm(1,0,5), 
       sigmatmp = rnorm(1,0,5)
       )
}

# set up model
jags <- jags.model(file = 'ttestlisa.jags',
                   data = jags.data,
                   inits = random.init, 
                   n.chains = 5)
# burnin
update(jags, n.iter= 10000)
mcmc.samples <- coda.samples(model = jags, 
                             variable.names = c( "delta", "mu", "sigma"),
                             n.iter = 100000, thining=5)
```

## a. Plot the posterior distribution of the δ parameter.
```{r delta}
mcmc.mat = as.matrix(mcmc.samples, chain=TRUE)
delta_samples= mcmc.mat[,"delta"]
#HPDinterval(mcmc.samples)
plotPost(delta_samples)
```

## b. Estimate the bayes factor between H0 : δ = 0 and H1 : δ ∼ Cauchy(0, 1) by using the Savage-Dickey method (see slides).
```{r savage}
fit.posterior <- logspline(delta_samples)
posterior <- dlogspline(0, fit.posterior) # this gives the pdf at point delta = 0
prior     <- dcauchy(0)                   # height of order--restricted prior at delta = 0
BF10      <- prior/posterior
BF10
```

## c. Use both a normal and an “ultrawide” rscale parameter for the Cauchy prior distribution.
```{r priors}
medium<- sqrt(2)/2
wide<- 1
ultrawide<- sqrt(2) 

# medium Prior
jags.data = list('x' = diffs,
                 'N' = length(diffs),
                 'rscale' = medium )
jags <- jags.model(file = 'ttestlisa.jags',
                   data = jags.data,
                   inits = random.init, 
                   n.chains = 5)
update(jags, n.iter= 10000)
mcmc.samples_m <- coda.samples(model = jags, 
                             variable.names = c( "delta", "mu", "sigma"),
                             n.iter = 100000, thining=5)

mcmc.mat_m = as.matrix(mcmc.samples_m, chain=TRUE)
delta_samples_m= mcmc.mat_m[,"delta"]
plotPost(delta_samples_m)

# Ultrawide Prior
jags.data = list('x' = diffs,
                 'N' = length(diffs),
                 'rscale' = ultrawide )
jags <- jags.model(file = 'ttestlisa.jags',
                   data = jags.data,
                   inits = random.init, 
                   n.chains = 5)
update(jags, n.iter= 10000)
mcmc.samples_xl <- coda.samples(model = jags, 
                             variable.names = c( "delta", "mu", "sigma"),
                             n.iter = 100000, thining=5)

mcmc.mat_xl = as.matrix(mcmc.samples_xl, chain=TRUE)
delta_samples_xl= mcmc.mat_xl[,"delta"]
plotPost(delta_samples_xl)

```


# Program version
```{r script_13}
sessionInfo()
````