---
title: 'Assignment 5: Modelling Linear Regression'
author: "Schwetlick"
date: '2018-05-02'
output: 
    html_document:
        toc: yes
        toc_depth: 3
        number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
library(tidyverse)
library(BayesFactor)
# setwd('/Users/lisa/Documents/BayesCourse/Potsdam-Bayes-2018/Lisa_Solutions')
library('rjags')
library('coda')
library('polspline')
source("kruschke-utilities.R")
```

Data: expenses.csv
A researcher is interested in the factors influencing the leisure expenses of 16- and 17-year olds. She collected data from 202 teenagers in order to predict leisure expenses in november (expenses_nov) from leisure expenses in July (expenses_jul), income from the students’ side occupation in november (salary_nov), and time spent on studying for high-school (studytime). The following figure depicts a possible regression model with one intercept (β0 or α) and three beta weights (β1, β2, β3) for the three dependent variables.

The priors of these parameters are normally distributed with Mi = 0 and large standard deviation (e.g. σ = 100). The measurements error of the dependent variable is normally distributed with a standard deviation σ (that is, the inverse of the precision parameter λ). The prior for σ is uniform (you might use here beta(1,1)).

Task: Please implement this regression model in JAGS and apply the data set above. It might be useful to take the JAGS model for a simple linear regression with a gamma distributed prior for the precision λ from the workshop (see github) and modify it accordingly. Please standardized the variables (scale command in R) before entering the data in the regression model.

## First, load and scale data. Also remove rows that include NA values
```{r data}
expe<-read.csv("../assignment/expenses.csv")
head(expe)

expe<- na.omit(expe)
expe<- as.data.frame(scale(expe[2:5]))
head(expe)
```

## Model
```{r model}
# prepare data and init list 
jags.data = list('N' = nrow(expe), 
                 'y' = expe$expenses_nov,
                 'x1' = expe$expenses_jul,
                 'x2' = expe$salary_nov,
                 'x3' = expe$studytime)

# initis random intits
random.init = function() {
  list(alpha = runif(1, -100, 100),
       beta1 = runif(1, -100, 100),
       beta2 = runif(1, -100, 100),
       beta3 = runif(1, -100, 100),
       lambda = rgamma(1, 0.01, 0.01))
}

# set up model
jags <- jags.model(file = 'linregLisa.jags',
                   data = jags.data,
                   inits = random.init, # or fix.inits
                   n.chains = 3,
                   n.adapt=500)

# burnin
update(jags, n.iter= 1000)

# sample theta values
mcmc.samples <- coda.samples(model = jags, 
                             variable.names = c( "alpha", "beta1", "beta2", "beta3", "sigma"),
                             n.iter = 30000, thining=20)

### parameter evaluation ###
# HDI (using coda package)
HPDinterval(mcmc.samples)

mcmc.mat = as.matrix(mcmc.samples, chain=TRUE)
summary(mcmc.mat)

par(mfrow=c(3,2)) 
plotPost(mcmc.mat[,"beta1"])#,75, main ="beta1")

plotPost(mcmc.mat[,"beta2"])#,75, main ="beta2")

plotPost(mcmc.mat[,"beta3"])#,75, main ="beta3")

plotPost(mcmc.mat[,"alpha"])#,75, main ="alpha")

plotPost(mcmc.mat[,"sigma"])#,75, main ="sigma")
```


# Program version
```{r script_13}
sessionInfo()
````